%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Enis Aras} \\ \vspace{1pt}
    \small 518-961-70-35 $|$ \href{mailto: arasenis@gmail.com}{\underline{arasenis@gmail.com}} $|$ 
    \href{https://linkedin.com/in/enis-aras}{\underline{linkedin.com/in/enis-aras}} $|$
    \href{https://github.com/enisaras}{\underline{github.com/enisaras}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Rensselaer Polytechnic Instute}{Troy, NY}
      {Bachelor of Science in Computer Science, Minor in Finance}{Fall 2020 -- May 2022}
      \resumeItemListStart
       \resumeItem{Learned about topics related to algorithms like dynamic programming, divide and conquer, NP-completeness and graph theory and designed many algorithms aimed to solve real life problems.}
       \resumeItem{Learned about Computer systems organization topics such as processors, memory, I/O with the help of C language as well as digital logic topics like Boolean algebra and logic gates.}
       \resumeItem{Learned about introductory Matrix Algebra topics like matrix algebra and systems of linear equations, vectors and linear transformations in $R^n$, eigenvectors and eigenvalues, and their applications in engineering and science.}
       \resumeItemListEnd
    \resumeSubheading
      {Hudson Valey Community College}{Troy, NY}
      {Associate's in Computer Science}{May 2019 -- May 2020}
        \resumeItemListStart
        \resumeItem{Learned about data structures like stacks, queues, lists, trees, and collections and their proper application using Java programming language.}
        \resumeItem{Learned about features of the C++ programming language including class design and data structures.}
       \resumeItem{Learned about topics including logic, relations, partial order, equivalence relations, lattices, Boolean algebra, graph theory, and predicate calculus. Gained a strong knowledge of proofs such as inductive, direct, contradiction, contraposition and exhaustion.}
       \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Developer at Quantify }{November 2020 -- Present}
      {Contract}{Niskayuna, NY}
      \resumeItemListStart
        \resumeItem{Worked with clients to convert their existing trading trading strategies into algorithms that can be automatically traded using platforms like QuantConnect and Alpaca.}
        \resumeItem{Visualized many trading strategies and back tested them using the platform TradingView and their scripting language Pine Script.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{The Archives(Under Development)} $|$ \emph{Python, AWS API Gateway, React, SQL}}{January 2021 -- Present}
          \resumeItemListStart
            \resumeItem{A Star Wars HTTP API containing all the data from the Star Wars lore including movies, TV shows and games.}
            \resumeItem{Aimed to be a fun and easy to use API for students and programmers new to using HTTP APIs.}
            \resumeItem{Complete documentation and many examples to help students and programmers get into the world of using APIs using data from the greatest franchise of all time.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Discord Betting Bot(Under Development)} $|$ \emph{Node, Discord.js, React, MangoDB}}{November 2020 -- Present}
          \resumeItemListStart
            \resumeItem{A virtual betting bot that uses real life sports betting odds to let users bet on their favorite teams.}
            \resumeItem{Features a complete MangoDB database that stores data ranging from each bet made to amount of coins each user currently has.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, SQL , JavaScript, HTML/CSS} \\
     \textbf{Frameworks}{: React, Node.js, Django, JUnit, JQuery} \\
     \textbf{Developer Tools}{: Git, TravisCI, Amazon Web Services, Vim, Visual Studio, PyCharm Eclipse, QuantConnect,Ubuntu} \\
     \textbf{Libraries}{: Pandas, NumPy, Matplotlib, Selenium}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
